\cvsection{Personal}

\begin{cventries}

	\cventry
	{} % Empty position
	{Highly self-motivated and work hard} % Project
	{} % Empty location
	{} % Empty date
	{
		\quad I have always been fascinated by the fundamental principles and laws that govern the universe. Driven by my curiosity, I embarked on a self-study journey, delving into various aspects of physics. Starting from classical mechanics, I progressively advanced my knowledge to encompass complex topics such as quantum field theory and general relativity. The study of physics, particularly as a computer science student, presented significant challenges due to the intricate mathematics involved. However, my passion and determination led me to invest several months of my free time to complete these courses successfully. \newline
		\quad The process of learning physics has been immensely fulfilling for me. Each new concept I grasped and each theory I understood brought me a sense of excitement and intellectual satisfaction. The profound understanding I gained from studying physics has expanded my horizons and opened up new avenues of thought. The feeling of discovering and comprehending the fundamental principles that govern our universe has been truly exhilarating. Not just limited to physics, I work hard for anything I am interested in. \newline
		% \quad I think my journey in mastering physics on my own demonstrates my strong self-learning abilities and the drive to pursue topics that genuinely captivate my interest. I believe this trait reflects my dedication, perseverance, and willingness to invest time and effort into areas that ignite my passion. \newline
	}
\end{cventries}
