\vspace{-2mm}
\cvsection{Selected Publications \large \href{https://scholar.google.com/citations?user=dR1J_4EAAAAJ&hl=zh-CN}{\textcolor{link}{[Google Scholar]}}}

\begin{cventries}

    \cventry
    {} % Empty position
    {\ } % Title
    {\ } % Empty location
    {} % Empty date
    {
        \vspace{-9mm}
        \begin{cvitemize2}
            \item \textbf{Wenhao Zheng}, Xinyu Ye, Peng Xia, Fang Wu, Linjie Li, Weitong Zhang, Lijuan Wang, Yejin Choi, Yun Li, Huaxiu Yao$^*$. ``The Agent's Marathon: Probing the Limits of Endurance in Long-Horizon Tasks,'' \textit{The International Conference on Learning Representations}, 2026, under review.
            \vspace{1mm}
            \item \textbf{Wenhao Zheng}, Jianshu She, Weitong Zhang, Yixiao Chen, Leshang Chen, Souvik Kundu, Eric P. Xing, Zhengzhong Liu, Qirong Ho, Hongyi Wang, Yun Li, Huaxiu Yao$^*$. ``CLEAR: A Cost-Aware Routing System for Edge-Cloud Language Model Collaborative Inference,'' \textit{The International Conference on Learning Representations}, 2026, under review.
            \vspace{1mm}
            \item \textbf{Wenhao Zheng$^\dagger$}, Yixiao Chen$^\dagger$, Weitong Zhang, Souvik Kundu, Yun Li, Zhengzhong Liu, Eric P. Xing, Hongyi Wang, Huaxiu Yao$^*$. ``CITER: Collaborative Inference for Efficient Large Language Model Decoding with Token-Level Routing,'' \textit{Conference on Language Modeling}, 2025. \href{https://openreview.net/forum?id=nqX9UYW9Af}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item \textbf{Wenhao Zheng$^\dagger$}, Liaoyaqi Wang$^\dagger$, Dongsheng Peng, Hongxia Xu, Hongtu Zhu, Tianfan Fu, Huaxiu Yao$^*$. ``LIFTED: Multimodal Clinical Trial Outcome Prediction via Large Language Models and Mixture-of-Experts,'' \textit{The Conference on Empirical Methods in Natural Language Processing}, 2025. \href{https://openreview.net/forum?id=HS4XgL5JyP}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Jianshu She, \textbf{Wenhao Zheng}, Zhengzhong Liu, Hongyi Wang, Eric Xing, Huaxiu Yao, Qirong Ho$^*$. ``Token Level Routing Inference System for Edge Devices,'' \textit{Annual Meeting of the Association for Computational Linguistics}, 2025. \href{https://aclanthology.org/2025.acl-demo.16/}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Zhaoyang Wang, Jinqi Jiang, Huichi Zhou, \textbf{Wenhao Zheng}, Xuchao Zhang, Chetan Bansal, Huaxiu Yao$^*$. ``Verifiable Format Control for Large Language Model Generations,'' \textit{Annual Meeting of the Association for Computational Linguistics}, 2025. \href{https://aclanthology.org/2025.findings-naacl.194/}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            % \item Peng Xia$^\dagger$, Siwei Han$^\dagger$, Shi Qiu$^\dagger$, Yiyang Zhou, Zhaoyang Wang, \textbf{Wenhao Zheng}, Zhaorun Chen, Chenhang Cui, Mingyu Ding, Linjie Li, Lijuan Wang, Huaxiu Yao$^*$, Tingting Chen, Zuozhu Liu, Danny Z. Chen, Ke Yao$^*$. ``MMIE: Massive Multimodal Interleaved Comprehension Benchmark for Large Vision-Language Models,'' \textit{International Conference on Learning Representations}, 2025. \href{https://openreview.net/forum?id=HnhNRrLPwm}{\textcolor{link}{[Link]}}
            % \vspace{1mm}
            % \item Yiyang Zhou, Zhaoyang Wang, Tianle Wang, Shangyu Xing, Peng Xia, Bo Li, Kaiyuan Zheng, Zijian Zhang, Zhaorun Chen, \textbf{Wenhao Zheng}, Xuchao Zhang, Chetan Bansal, Weitong Zhang, Ying Wei, Mohit Bansal, Huaxiu Yao$^*$. ``AnyPrefer: An Automatic Framework for Preference Data Synthesis,'' \textit{International Conference on Learning Representations}, 2025. \href{https://openreview.net/forum?id=WpZyPk79Fu}{\textcolor{link}{[Link]}}
            % \vspace{1mm}
            \item Tony Lee$^\dagger$, Haoqin Tu$^\dagger$, Chi Heem Wong$^\dagger$, \textbf{Wenhao Zheng}, Yiyang Zhou, Yifan Mai, Josselin Somerville Roberts, Michihiro Yasunaga, Huaxiu Yao, Cihang Xie, Percy Liang$^*$. ``VHELM: A Holistic Evaluation of Vision Language Models,'' \textit{Conference on Neural Information Processing Systems}, 2024. \href{https://crfm.stanford.edu/helm/vhelm/latest/}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            % \item Peng Xia$^\dagger$, Ming Hu$^\dagger$, Feilong Tang, Wenxue Li, \textbf{Wenhao Zheng}, Lie Ju, Peibo Duan, Huaxiu Yao$^*$, Zongyuan Ge$^*$. ``Generalizing to Unseen Domains in Diabetic Retinopathy with Disentangled Representations,'' \textit{Medical Image Computing and Computer Assisted Intervention}, 2024. \href{https://link.springer.com/chapter/10.1007/978-3-031-72117-5_40}{\textcolor{link}{[Link]}}
            % \vspace{1mm}
            % \item Peng Xia, Ze Chen, Juanxi Tian$^\dagger$, Yangrui Gong$^\dagger$, Ruibo Hou, Yue Xu, Zhenbang Wu, Zhiyuan Fan, Yiyang Zhou, Kangyu Zhu, \textbf{Wenhao Zheng}, Zhaoyang Wang, Xiao Wang, Xuchao Zhang, Chetan Bansal, Marc Niethammer, Junzhou Huang, Hongtu Zhu, Yun Li, Jimeng Sun, Zongyuan Ge$^*$, Gang Li, James Zou, Huaxiu Yao$^*$. ``CARES: A Comprehensive Benchmark of Trustworthiness in Medical Vision Language Models,'' \textit{Conference on Neural Information Processing Systems}, 2024. \href{https://proceedings.neurips.cc/paper_files/paper/2024/file/fde7f40f8ced5735006810534dc66b33-Paper-Datasets_and_Benchmarks_Track.pdf}{\textcolor{link}{[Link]}}
            % \vspace{1mm}
            \item \textbf{Wenhao Zheng}, Jintai Chen, Kai Zhang, Jiahuan Yan, Jinhong Wang, Yi Cheng, Bang Du, Danny Z. Chen, Honghao Gao$^*$, Jian Wu, Hongxia Xu$^*$. ``Polygonal Approximation Learning for Convex Object Segmentation in Biomedical Images with Bounding Box Supervision,'' \textit{IEEE Journal of Biomedical and Health Informatics}, 2023. \href{https://ieeexplore.ieee.org/document/10354298}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Jinhong Wang$^\dagger$, Zhe Xu$^\dagger$, \textbf{Wenhao Zheng$^\dagger$}, Haochao Ying$^*$, Tingting Chen, Zuozhu Liu, Danny Z. Chen, Ke Yao$^*$, Jian Wu. ``A Transformer-based Knowledge DistillationNetwork for Cortical Cataract Grading,'' \textit{IEEE Transactions on Medical Imaging}, 2023. \href{https://ieeexplore.ieee.org/abstract/document/10294274}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Tingting Chen$^\dagger$, \textbf{Wenhao Zheng$^\dagger$}, Haochao Ying, Xiangyu Tan, Kexin Li, Xiaoping Li, Danny Z. Chen, Jian Wu$^*$. ``A Task Decomposing and Cell Comparing Method for Cervical Lesion Cell Detection,'' \textit{IEEE Transactions on Medical Imaging}, 2022. \href{https://ieeexplore.ieee.org/document/9744114}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Yi Cheng, Haochao Ying$^*$, Renjun Hu, Jinhong Wang, \textbf{Wenhao Zheng}, Xiao Zhang, Danny Z. Chen, Jian Wu. ``Robust Image Ordinal Regression with Controllable Image Generation,'' \textit{International Joint Conference on Artificial Intelligence}, 2023. \href{https://dl.acm.org/doi/abs/10.24963/ijcai.2023/70}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Tingting Chen, \textbf{Wenhao Zheng}, Heping Hu, Chunhua Luo, Jintai Chen, Chunnv Yuan, Weiguo Lu, Danny Z. Chen, Honghao Gao$^*$ and Jian Wu$^*$. ``A Corresponding Region Fusion Framework for Multi-modal Cervical Lesion Detection,'' \textit{IEEE/ACM Transactions on Computational Biology and Bioinformatics}, 2022. \href{https://ieeexplore.ieee.org/document/9784879}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Jinhong Wang$^\dagger$, Jingwen Wang$^\dagger$, Tingting Chen, \textbf{Wenhao Zheng}, Zhe Xu, Xingdi Wu, Wen Xu$^*$, Haochao Ying$^*$, Danny Z. Chen, and Jian Wu. ``CTT-Net: A Multi-view Cross-token Transformer for Cataract Postoperative Visual Acuity Prediction,'' \textit{IEEE International Conference on Bioinformatics and Biomedicine}, 2022. \href{https://ieeexplore.ieee.org/document/9995392}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Tingting Chen$^\dagger$, Yi Cheng$^\dagger$, Jinhong Wang, Zhaoxia Yang, \textbf{Wenhao Zheng}, Danny Z. Chen, and Jian Wu$^*$. ``Automating Blastocyst Formation and Quality Prediction in Time-Lapse Imaging with Adaptive Key Frame Selection,'' \textit{Medical Image Computing and Computer Assisted Intervention}, 2022. \href{https://link.springer.com/chapter/10.1007/978-3-031-16440-8_43}{\textcolor{link}{[Link]}}
        \end{cvitemize2}
    }

\end{cventries}
